---
title: "Data_Preprocessing"
author: "Xiaowo Sun"
date: "4/18/2019"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

```{r results='hide', message=FALSE, warning=FALSE}
library(tibble)
library(tidyverse) 
library(dplyr)
library(Hmisc)
library(funModeling)
library(stringr)
library(readr)
library(mi)
library(ggplot2)
library(plotly)
library(extracat)
```

```{r}
df = read.csv("../../DOHMH_New_York_City_Restaurant_Inspection_Results.csv", 
              na.strings=c(c("", "N/A"), "NA"), stringsAsFactors=FALSE)
```

```{r}
head(df,10)
```

```{r}
# convert data type
df$CAMIS = as.character(df$CAMIS)
df$ZIPCODE = as.character(df$ZIPCODE)
# ignore restaurants that have not been inspected
df_inspected = df[df$INSPECTION.DATE!="01/01/1900",]
```

```{r}
basic_eda <- function(data)
{
  glimpse(data)
  df_status(data)
  freq(data) 
  profiling_num(data)
  plot_num(data)
  describe(data)
}

basic_eda(df_inspected)
```

```{r}
# check missing values before further preprocessing
colSums(is.na(df_inspected)) %>%
  sort(decreasing = TRUE)
```

### Check Each Variable
#### BORO
Replace the values of "missing" with true BORO by checking other location related variables on Google Map.
```{r}
df_inspected[df_inspected$BORO=="Missing",]
unique(df_inspected[df_inspected$BORO=="Missing",]$CAMIS)

df_inspected$BORO[df_inspected$CAMIS == "40883586"] <- "MANHATTAN"
df_inspected$BORO[df_inspected$CAMIS == "50005059"] <- "BROOKLYN"
df_inspected$BORO[df_inspected$CAMIS == "50005134"] <- "BROOKLYN"
df_inspected$BORO[df_inspected$CAMIS == "50011555"] <- "MANHATTAN"
df_inspected$BORO[df_inspected$CAMIS == "50043829"] <- "BROOKLYN"
df_inspected$BORO[df_inspected$CAMIS == "50047425"] <- "MANHATTAN"
df_inspected$BORO[df_inspected$CAMIS == "50049804"] <- "BROOKLYN"
df_inspected$BORO[df_inspected$CAMIS == "50060598"] <- "MANHATTAN"

freq(df_inspected$BORO) 
```

#### ZIPCODE
```{r}
df_inspected[is.na(df_inspected$ZIPCODE),]
unique(df_inspected[is.na(df_inspected$ZIPCODE),]$CAMIS)
```

#### PHONE
Replace illogical values with NA.
```{r}
sp_char <- "_"
df_inspected$PHONE  <- gsub(sp_char, "", df_inspected$PHONE)
df_inspected$PHONE[nchar(df_inspected$PHONE) != 10] <- NA 
df_inspected$PHONE[df_inspected$PHONE=='0000000000'] <- NA
```

#### CUISINE.DESCRIPTION
Modify the description for some categories
```{r}
freq(df_inspected$CUISINE.DESCRIPTION)
```
```{r}
df_inspected$CUISINE.DESCRIPTION[df_inspected$CUISINE.DESCRIPTION == "Café/Coffee/Tea"] <- "Cafe/Coffee/Tea"
```

#### SCORE
Check and replace illogical values (-1) with NA, as the lowest score can only be 0.
```{r}
boxplot(df_inspected$SCORE)
summary(df_inspected$SCORE)
```

```{r}
df_inspected$SCORE[!is.na(df_inspected$SCORE) & df_inspected$SCORE == -1] <- NA
```

#### Grade
```{r}
df_inspected[!is.na(df_inspected$GRADE) & (df_inspected$GRADE == "G"),]
```

```{r}
df_inspected[!is.na(df_inspected$GRADE) & (df_inspected$GRADE %in% c("Z","P","G")),]$GRADE <- "Grade Pending"
```


```{r}
freq(df_inspected$GRADE)
```




```{r}
write.csv(df_inspected, file="cleaned.csv", row.names=FALSE)
```

```{r}
df_inspected
```

#### Create Variables (for potential use)
```{r}
df_inspected$INSPECTION.DATE.convert = as.Date(df_inspected$INSPECTION.DATE, "%m/%d/%Y")
df_inspected$GRADE.DATE.convert = as.Date(df_inspected$GRADE.DATE, "%m/%d/%Y")
df_inspected$Address = paste(df_inspected$BUILDING, df_inspected$STREET, sep=" ")
df_inspected$Address = paste(df_inspected$Address, df_inspected$BORO, sep=", ")
df_inspected$State <- paste('NY', df_inspected$ZIPCODE, sep=" ")
df_inspected$Address = paste(df_inspected$Address, df_inspected$State, sep=", ")
```

```{r}
head(df_inspected)
```

```{r}
min(df_inspected$INSPECTION.DATE.convert)
min(df_inspected[!is.na(df_inspected$GRADE.DATE.convert),]$GRADE.DATE.convert)
```



```{r}
write.csv(df_inspected, file="cleaned_add.csv", row.names=FALSE)
```

#### Recent Grade
```{r}
Inspections <- df_inspected %>%
    filter(((`INSPECTION.TYPE` %in% 
            c('Cycle Inspection / Re-inspection'
              ,'Pre-permit (Operational) / Re-inspection')
          |(`INSPECTION.TYPE` %in%
              c('Cycle Inspection / Initial Inspection'
                ,'Pre-permit (Operational) / Initial Inspection')) 
          & SCORE <= 13)
         | (`INSPECTION.TYPE` %in%  
              c('Pre-permit (Operational) / Reopening Inspection'
                ,'Cycle Inspection / Reopening Inspection')))
         & GRADE %in% c('A', 'B', 'C', 'Grade Pending')) %>%
  select(CAMIS,`INSPECTION.DATE`)

#Select distinct inspections
Inspections_Distinct <- distinct(Inspections)

#Select most recent inspection date
MostRecentInsp <- Inspections_Distinct %>%
  group_by(CAMIS) %>%
  slice(which.max(as.Date(`INSPECTION.DATE`,'%m/%d/%Y')))

#Join most recent inspection with original dataset
inner_join(df_inspected, MostRecentInsp, by = "CAMIS","INSPECTION.DATE")

#Select restaurant inspection data based on most recent inspection date
Final <- df_inspected %>% inner_join(MostRecentInsp) %>%
    filter((`INSPECTION.TYPE` %in% 
            c('Cycle Inspection / Re-inspection'
              ,'Pre-permit (Operational) / Re-inspection'
              , 'Pre-permit (Operational) / Reopening Inspection' 
              ,'Cycle Inspection / Reopening Inspection')
          |(`INSPECTION.TYPE` %in%
              c('Cycle Inspection / Initial Inspection'
                ,'Pre-permit (Operational) / Initial Inspection')) 
          & SCORE <= 13)) %>%
  
  select(CAMIS,DBA,Address,BORO,BUILDING,STREET,ZIPCODE,`CUISINE.DESCRIPTION`,
         `INSPECTION.DATE`,GRADE,`INSPECTION.TYPE`,SCORE)

#,PHONE,ACTION,`VIOLATION.CODE`,`VIOLATION.DESCRIPTION`,`CRITICAL.FLAG`

#Select distinct restaurant inspection data
Final <- distinct(Final)

write.csv(Final, file="recent_grade_per_restaurant.csv", row.names=FALSE)

```

```{r}
Inspections <- df_inspected %>%
    filter(((`INSPECTION.TYPE` %in% 
            c('Cycle Inspection / Re-inspection'
              ,'Pre-permit (Operational) / Re-inspection')
          |(`INSPECTION.TYPE` %in%
              c('Cycle Inspection / Initial Inspection'
                ,'Pre-permit (Operational) / Initial Inspection')) 
          & SCORE <= 13)
         | (`INSPECTION.TYPE` %in%  
              c('Pre-permit (Operational) / Reopening Inspection'
                ,'Cycle Inspection / Reopening Inspection')))
         & GRADE %in% c('A', 'B', 'C', 'Grade Pending')) %>%
  select(CAMIS,`INSPECTION.DATE`)

#Select distinct inspections
Inspections_Distinct <- distinct(Inspections)

#Select most recent inspection date
MostRecentInsp <- Inspections_Distinct %>%
  group_by(CAMIS) %>%
  slice(which.max(as.Date(`INSPECTION.DATE`,'%m/%d/%Y')))

#Join most recent inspection with original dataset
inner_join(df_inspected, MostRecentInsp, by = "CAMIS","INSPECTION.DATE")

#Select restaurant inspection data based on most recent inspection date
Final_all <- df_inspected %>% inner_join(MostRecentInsp) %>%
    filter((`INSPECTION.TYPE` %in% 
            c('Cycle Inspection / Re-inspection'
              ,'Pre-permit (Operational) / Re-inspection'
              , 'Pre-permit (Operational) / Reopening Inspection' 
              ,'Cycle Inspection / Reopening Inspection')
          |(`INSPECTION.TYPE` %in%
              c('Cycle Inspection / Initial Inspection'
                ,'Pre-permit (Operational) / Initial Inspection')) 
          & SCORE <= 13)) %>%
  
  select(CAMIS,DBA,Address,BORO,BUILDING,STREET,ZIPCODE,`CUISINE.DESCRIPTION`,PHONE,ACTION,`VIOLATION.CODE`,`VIOLATION.DESCRIPTION`,`CRITICAL.FLAG`,`INSPECTION.DATE`,GRADE,`INSPECTION.TYPE`,SCORE)

#Select distinct restaurant inspection data
Final_all <- distinct(Final_all)

write.csv(Final_all, file="recent_grade_per_restaurant_ALL.csv", row.names=FALSE)

```


```{r}
ggplot(Final, aes(GRADE)) + 
  geom_bar(fill = "#52c7cb") + 
  xlab("Grade") + 
  ylab("Number of Restaurants") +
  ggtitle("Number of Restaurants by Grades in NYC")
```

```{r}
basic_eda(Final)
```


```{r}
basic_eda(Final)
```



```{r}

```

# Missing Value
```{r}
colSums(is.na(df_inspected)) %>%
  sort(decreasing = TRUE)
```

```{r}
df_na <- df_inspected[,1:18]

missing.values <- df_na %>%
  gather(key = "key", value = "val") %>%
  mutate(isna = is.na(val)) %>%
  group_by(key) %>%
  mutate(total = n()) %>%
  group_by(key, total, isna) %>%
  summarise(num.isna = n()) %>%
  mutate(pct = num.isna / total * 100)


levels <-
    (missing.values  %>% filter(isna == T) %>% arrange(desc(pct)))$key

percentage.plot <- missing.values %>%
      ggplot() +
        geom_bar(aes(x = reorder(key, desc(pct)), 
                     y = pct, fill=isna), 
                 stat = 'identity', alpha=0.8) +
      scale_x_discrete(limits = levels) +
      scale_fill_manual(name = "", 
                        values = c('steelblue', 'tomato3'), labels = c("Present", "Missing")) +
      coord_flip() +
      labs(title = "Percentage of missing values", x =
             'Variable', y = "% of missing values")

ggplotly(percentage.plot)
```


```{r}
df_na <- df_inspected[, 1:18]
df_na
```

```{r}
x <- missing_data.frame(df_na[, 9:18])
class(x)
x@patterns
levels(x@patterns)
summary(x@patterns)
```

```{r, fig.height=10, fig.width=12}
visna(df_na, sort = "b")
```


